A thesis draft

### 2018-09-07 draft.tex
Add abstract

 In the modern mobile networking, these is the continuous necessity to 
improve the overall speed connection: important goals are low latency and a 
good throughtput. Mobile data is continuously sourging every year, with the 
backbones having more traffic to process. In this context, in-hardware backbone 
solutions are becoming less efficent. Their time-to-deploy, in fact, is very 
high compared to the requirement of the network. With this trend, in-hardware 
solutions will not be able to keep the

>>>>

 In the modern mobile networking, these is a continuous necessity to 
improve the overall speed connection: important goals are low latency and a 
high throughtput. Mobile traffic is continuously surging every year, with 
the backbones having more data to process. In this context, in-hardware 
backbone solutions are becoming less efficent. Their time-to-deploy, in fact, is 
very high compared to the requirements of the network. With this trend, 
in-hardware solutions will not be able to keep up. Is with this considerations 
that software solutions are being proposed to become the new way to deploy 
network components. While less efficent, they are faster to bring them up. On 
top of that, new virtualization technologies such as Docker are becoming more 
and more mature to be employable for large-scale production environments, where 
new frameworks, called orchestrators, allow to easily manage the application 
lifecyle, i.e. deployment, scale up/down and finally, removal.
